---
title: "SusDat_Updated_01032018"
author: "AB/CP"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    self_contained: yes
    widescreen: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Pre-Processing

## Load
```{r}
NORMAN <- read.table(
  system.file("extdata/SusDat_Updated_01032018_ID_SMILES.txt",
                                 package = "UVPD"), 
                     sep="\t", header=TRUE)
``` 



## Data Cleaning


`NA`

## Some basic Statistics

SMILES length
```{r fig.retina=3, fig.width=8, fig.height=4}
hist(nchar(as.character(NORMAN$SMILES)))
```


## Sampling
```{r}
set.seed(5)
n.size <- 2000
smp <- sample(nrow(NORMAN), n.size)
NORMAN.smp <- NORMAN[smp, ]
NORMAN.smp$clusterID <- NA
```

## Add Ground Truth {.smaller}

```{r echo=FALSE, eval=FALSE}
GT2 <- data.frame(
  ID = c("Metolachlor", "Metolachlor ESA", "Clofibric acid", "Carbamazepine", "Carbamazepine-10,11-epoxide", "Carbamazepine-9-carboxaldehyde", "OLEYL ARACHIDATE", "OLEYL ACETATE"),
  SMILES = c("CCc1cccc(c1N(C(C)COC)C(=O)CCl)C", "O=S(=O)(O)CC(=O)N(C(C)COC)c1c(CC)cccc1C", "CC(C)(Oc1ccc(Cl)cc1)C(=O)O", "N1(c2c(cccc2)C=Cc2c1cccc2)C(=O)N", "NC(=O)N1c2ccccc2C2OC2c2ccccc12", "NC(=O)N1c2ccccc2C(C=O)c2ccccc12", "CCCCCCCCCCCCCCCCCCCC(=O)OCCCCCCCC/C=C\\CCCCCCCC", "CCCCCCCC/C=C\\CCCCCCCCOC(=O)C"))
```

```{r}
GT <- read.table(
  system.file("extdata/GroundTruth.csv",  package = "UVPD"), 
                     sep="\t", header=TRUE, fill=TRUE)
table(GT$clusterID)
```

```{r}
NORMAN.smp <- rbind(NORMAN.smp, GT)
```

## List {.smaller}

```{r}
knitr::kable(tail(NORMAN.smp))
```

## use rcdk 

```{r}
library(rcdk)
mols <- parse.smiles(as.character(NORMAN.smp$SMILES))

for (i in mols) {
  try(do.aromaticity(i))
  try(do.typing(i))
  try(do.isotopes(i))
}

show(mols[length(mols)])
show(mols[length(mols)-1])
```




## compute fingerprint; 

```{r}
fps.extended <- lapply(mols, function(x){try(get.fingerprint(x, type='extended'))})
table(sapply(fps.extended, class))

fps.pubchem <- lapply(mols, function(x){try(get.fingerprint(x, type='pubchem'))})
table(sapply(fps.pubchem, class))
```

## idx.corrupt contains corrupt smile codes?


```{r}
idx.corrupt.extended <- which(sapply(fps.extended, class) != "fingerprint")
idx.correct.extended <- which(sapply(fps.extended, class) == "fingerprint")
fps.extended <- fps.extended[idx.correct.extended]
tail(idx.correct.extended,2)
```


```{r}
idx.corrupt.pubchem <- which(sapply(fps.pubchem, class) != "fingerprint")
idx.correct.pubchem <- which(sapply(fps.pubchem, class) == "fingerprint")
fps.pubchem <- fps.pubchem[idx.correct.pubchem]

stopifnot(identical(idx.correct.extended, idx.correct.pubchem))
NORMAN.smp <- NORMAN.smp[idx.correct.extended,]
NORMAN.smp$SMILES[c(nrow(NORMAN.smp)-1, nrow(NORMAN.smp))]
```




## Compute Distance Matrix

```{r}
fp.extended.tanimoto <- fingerprint::fp.sim.matrix(fps.extended, method='tanimoto')
fp.pubchem.tanimoto <- fingerprint::fp.sim.matrix(fps.pubchem, method='tanimoto')

dim(fp.extended.tanimoto);
fp.dist.extended <- as.dist(1 - (fp.extended.tanimoto))
fp.dist.pubchem <- as.dist(1 - (fp.pubchem.tanimoto))
save(NORMAN.smp, fp.dist.extended, fp.dist.pubchem, file="/tmp/UVPD_fp_dist.RData")
```

## Sanity checks

```{r}
```

## Some distance statistics
```{r fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1, 2))
hist(fp.dist.extended)
hist(fp.dist.pubchem)
```

## Sanity checks 

```{r fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1,2))
image(as.matrix(fp.dist.extended))
image(as.matrix(fp.dist.pubchem))
```


# Clustering


## hclust

```{r fig.retina=3, fig.width=8, fig.height=4}
# plot(hc <- hclust(fp.dist))
```


## kmeans

```{r}
kmc.extended <- kmeans(fp.dist.extended, 10, iter.max = 100)
table(kmc.extended$cluster)
```
```{r}
kmc.pubchem <- kmeans(fp.dist.pubchem, 10, iter.max = 100)
table(kmc.pubchem$cluster)
```


## write results

```{r}
NORMAN.smp$kmc.extended <- kmc.extended$cluster
NORMAN.smp$kmc.pubchem <- kmc.pubchem$cluster
```

```{r}
knitr::kable(head(NORMAN.smp))
```

# Visualization 


## using PCA {.smaller}

```{r fig.retina=3, fig.width=8, fig.height=6, echo=FALSE}
op <- par(mfrow = c(1, 2))
pcr.extended <- prcomp(fp.dist.extended)
pcr.pubchem <- prcomp(fp.dist.pubchem)
plot(pcr.extended)
plot(pcr.pubchem)
```

## plot pc2 versus pc1 {.smaller}
```{r fig.retina=3, fig.width=8, fig.height=5, echo=FALSE, eval = TRUE}
rb <- rainbow(11, alpha = 0.5)
op <- par(mfrow = c(1, 2))
plot(pcr.extended$x[,1], pcr.extended$x[,2],
    pch = 16,
     cex = 0.5,
     col=rb[kmc.extended$cluster])

text(pcr.extended$x[,1], pcr.extended$x[,2], 
     NORMAN.smp$ID[as.numeric(names(pcr.extended$x[, 1]))], 
     cex=0.3,
     pos=3, 
     col=rb[kmc.extended$cluster])

text(pcr.extended$x[,1], pcr.extended$x[,2], 
     NORMAN.smp$clusterID[as.numeric(names(pcr.extended$x[, 1]))], 
     cex=0.4,
     pos=1, 
     col='black')
###

plot(pcr.pubchem$x[,1], pcr.pubchem$x[,2],
     pch = 16,
     cex = 0.5,
     col = rb[kmc.pubchem$cluster])

text(pcr.pubchem$x[,1], pcr.pubchem$x[,2], 
     NORMAN.smp$ID[as.numeric(names(pcr.pubchem$x[, 1]))], 
     cex=0.3,
     pos=3, 
     col=rb[kmc.pubchem$cluster])

text(pcr.pubchem$x[,1], pcr.pubchem$x[,2], 
     NORMAN.smp$clusterID[as.numeric(names(pcr.pubchem$x[, 1]))], 
     cex=0.4,
     pos=1, 
     col='black')
```
