---
title: "SusDat_Updated_01032018"
author: "AB/CP"
date: "`r Sys.Date()`"
output: tint::tintHtml
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Pre-Processing

## Load
```{r}
NORMAN <- read.table(
  system.file("extdata/SusDat_Updated_01032018_ID_SMILES.txt",
                                 package = "UVPD"), 
                     sep="\t", header=TRUE)
``` 



## Data Cleaning


`NA`

## Some basic Statistics

SMILES length
```{r fig.retina=3, fig.width=8, fig.height=4}
hist(nchar(as.character(NORMAN$SMILES)))
```


## Sampling
```{r}
set.seed(5)
n.size <- 2000
ncluster <- 6
smp <- sample(nrow(NORMAN), n.size)
NORMAN.smp <- NORMAN[smp, ]
NORMAN.smp$clusterID <- NA
```

## Add Ground Truth {.smaller}

```{r echo=FALSE, eval=FALSE}
GT2 <- data.frame(
  ID = c("Metolachlor", "Metolachlor ESA", "Clofibric acid", "Carbamazepine", "Carbamazepine-10,11-epoxide", "Carbamazepine-9-carboxaldehyde", "OLEYL ARACHIDATE", "OLEYL ACETATE"),
  SMILES = c("CCc1cccc(c1N(C(C)COC)C(=O)CCl)C", "O=S(=O)(O)CC(=O)N(C(C)COC)c1c(CC)cccc1C", "CC(C)(Oc1ccc(Cl)cc1)C(=O)O", "N1(c2c(cccc2)C=Cc2c1cccc2)C(=O)N", "NC(=O)N1c2ccccc2C2OC2c2ccccc12", "NC(=O)N1c2ccccc2C(C=O)c2ccccc12", "CCCCCCCCCCCCCCCCCCCC(=O)OCCCCCCCC/C=C\\CCCCCCCC", "CCCCCCCC/C=C\\CCCCCCCCOC(=O)C"))
```

```{r load_ground_truth}
GT <- read.table(
  system.file("extdata/GroundTruth.csv",  package = "UVPD"), 
                     sep="\t", header=TRUE, fill=TRUE)
table(GT$clusterID)
```

```{r}
NORMAN.smp <- rbind(NORMAN.smp, GT)
```

## List {.smaller}

```{r}
knitr::kable(tail(NORMAN.smp))
```

## use rcdk 

```{r}
library(rcdk)
mols <- parse.smiles(as.character(NORMAN.smp$SMILES))

for (i in mols) {
  try(do.aromaticity(i))
  try(do.typing(i))
  try(do.isotopes(i))
}

show(mols[length(mols)])
show(mols[length(mols)-1])
```




## compute fingerprint; 

```{r}
fps.extended <- lapply(mols, function(x){try(get.fingerprint(x, type='extended'))})
table(sapply(fps.extended, class))

fps.pubchem <- lapply(mols, function(x){try(get.fingerprint(x, type='pubchem'))})


table(sapply(fps.pubchem, class))
```

## idx.corrupt contains corrupt smile codes?


```{r}
idx.corrupt.extended <- which(sapply(fps.extended, class) != "fingerprint")
idx.correct.extended <- which(sapply(fps.extended, class) == "fingerprint")
fps.extended <- fps.extended[idx.correct.extended]
tail(idx.correct.extended,2)
```


```{r}
idx.corrupt.pubchem <- which(sapply(fps.pubchem, class) != "fingerprint")
idx.correct.pubchem <- which(sapply(fps.pubchem, class) == "fingerprint")
fps.pubchem <- fps.pubchem[idx.correct.pubchem]

stopifnot(identical(idx.correct.extended, idx.correct.pubchem))
NORMAN.smp <- NORMAN.smp[idx.correct.extended,]
NORMAN.smp$SMILES[c(nrow(NORMAN.smp)-1, nrow(NORMAN.smp))]
```




## Compute Distance Matrix

```{r}
#fpmat.pubchem <- fp.to.matrix(fps.pubchem)   
fp.extended.tanimoto <- fingerprint::fp.sim.matrix(fps.extended, method='tanimoto')
fp.pubchem.tanimoto <- fingerprint::fp.sim.matrix(fps.pubchem, method='tanimoto')

dim(fp.extended.tanimoto);
fp.dist.extended <- as.dist(1 - (fp.extended.tanimoto))
fp.dist.pubchem <- as.dist(1 - (fp.pubchem.tanimoto))
save(NORMAN.smp, fp.dist.extended, fp.dist.pubchem, file="/tmp/UVPD_fp_dist.RData")
```

## Sanity checks

```{r}
```

## Some distance statistics
```{r fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1, 2))
hist(fp.dist.extended)
hist(fp.dist.pubchem)
```

## Sanity checks 

```{r fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1, 2))
image(as.matrix(fp.dist.extended))
image(as.matrix(fp.dist.pubchem))
```


# Clustering

```{r}
(ncluster)
```

## hclust

```{r fig.retina=3, fig.width=8, fig.height=4}
hc.extended <- hclust(fp.dist.extended)#, hang = -0.01, cex = 0.7)
hc.pubchem <- hclust(fp.dist.pubchem) #, hang = -0.01, cex = 0.7)
```


## kmeans

```{r}
set.seed(1) ## kmeans uses a random start
kmc.extended <- kmeans(fp.dist.extended, center = ncluster, iter.max = 100)
table(kmc.extended$cluster)
```
```{r}
set.seed(1) ## kmeans uses a random start
kmc.pubchem <- kmeans(fp.dist.pubchem, center = ncluster, iter.max = 100)
table(kmc.pubchem$cluster)
```


## Determine number of clusters


```{r Determine_N fig.retina=3}


tot.withinss <- sapply(1:14, function(n){
 km <- kmeans(fp.dist.pubchem, center = n)
 km$tot.withinss	
})
```

## write results

```{r}
NORMAN.smp$kmc.extended <- kmc.extended$cluster
NORMAN.smp$kmc.pubchem <- kmc.pubchem$cluster
NORMAN.smp$hc.extended  <- cutree(hc.extended, k = ncluster)
NORMAN.smp$hc.pubchem  <- cutree(hc.pubchem, k = ncluster)
```

```{r}
knitr::kable(head(NORMAN.smp, 20))
```

# Visualization 


## using PCA {.smaller}

Please note: the PCR is only used for a projection into the 2D.
Here we have the scores:
```{r fig.retina=3, fig.width=8, fig.height=6, echo=FALSE}
op <- par(mfrow = c(1, 2))
pcr.extended <- prcomp(fp.dist.extended)
pcr.pubchem <- prcomp(fp.dist.pubchem)
plot(pcr.extended)
plot(pcr.pubchem)
```


## plot pc2 versus pc1 {.smaller}

```{r fig.retina=3, fig.width=10, fig.height=10, echo=FALSE, eval = TRUE}
rb <- rainbow(11, alpha = 0.5)
op <- par(mfrow = c(2, 2))

rv <- lapply(c('hc.extended', 'kmc.extended'), 
             function(clusterMethod){
               plot(pcr.extended$x[,1], pcr.extended$x[,2],
                    pch = 16,
                    main = clusterMethod,
                    cex = 0.5,
                    col = rb[NORMAN.smp[,clusterMethod]])
               
               text(pcr.extended$x[,1], pcr.extended$x[,2], 
                    NORMAN.smp$ID[as.numeric(names(pcr.extended$x[, 1]))], 
                    cex = 0.3,
                    pos = 3, 
                    col = rb[NORMAN.smp[, clusterMethod]])
               
               text(pcr.extended$x[,1], pcr.extended$x[,2], 
                    NORMAN.smp$clusterID[as.numeric(names(pcr.extended$x[, 1]))], 
                    cex = 0.4,
                    pos = 1, 
                    col = 'black')
               
             })

rv <- lapply(c( 'hc.pubchem',  'kmc.pubchem'), 
             function(clusterMethod){
               plot(pcr.pubchem$x[,1], pcr.pubchem$x[,2],
                    pch = 16,
                    main = clusterMethod,
                    cex = 0.5,
                    col = rb[NORMAN.smp[,clusterMethod]])
               
               text(pcr.pubchem$x[,1], pcr.pubchem$x[,2], 
                    NORMAN.smp$ID[as.numeric(names(pcr.pubchem$x[, 1]))], 
                    cex = 0.3,
                    pos = 3, 
                    col = rb[NORMAN.smp[, clusterMethod]])
               
               text(pcr.pubchem$x[,1], pcr.pubchem$x[,2], 
                    NORMAN.smp$clusterID[as.numeric(names(pcr.pubchem$x[, 1]))], 
                    cex = 0.4,
                    pos = 1, 
                    col = 'black')
               
             })

     
###
```


## Evaluation of the clustering

### Frequency
```{r}
lapply(c('hc.extended', 'hc.pubchem', 'kmc.extended', 'kmc.pubchem'), function(clusterMethod){table(NORMAN.smp[,clusterMethod])})
```

### Summary

```{r}
summary(hc.pubchem)
summary(hc.extended)
summary(kmc.pubchem)
summary(kmc.extended)
```



# SOM


## 

```{r}
fpmat_pubchem <- fp.to.matrix(fps.pubchem) 
```

```{r}
cm <- rainbow(ncluster, alpha=0.5)
G <-somgrid(14, 14, "hexagonal")
S <- som(fingerprint::fp.to.matrix(fps.pubchem), grid=G)


plot(S, type = 'changes')
plot(S, type="mapping", col = cm[kmc.pubchem$cluster], pch=16)
add.cluster.boundaries(S, kmc.pubchem$cluster)

```

```{r}
library(kohonen)
cm<-rainbow(4)
S <- som(scale(iris[,c(1,2,3,4)]), grid=somgrid(topo = "hexagonal"));
C <- as.integer(iris[,5])
plot.kohonen(S, type="mapping", col = cm[C]); 
add.cluster.boundaries(S, C)
```