---
title: "Computer in-silico fragment and match"
author: "AB/CP"
output:
  html_document:
    toc_float: true
    toc: true
    number_sections: true
    theme: united
bibliography: uvpd.bib
---

# 2019-03-14 

session @ fgcz, AB/CP

- site note: Metabolmics 


TODO:

- MetFragR R package https://github.com/ipb-halle/MetFragR
  * compute in-silico fragments (CP)
  
https://github.com/ipb-halle/MetFragR/blob/9e482f6f6cb3cb6aa07af779d9acc7d6ff757f5f/metfRag/R/fragment.R#L11


```{r}
library(metfRag)

smiles <- "CC(C)(C)C(O)C(OC1=CC=C(Cl)C=C1)N1C=NC=N1"
molecule<-parse.smiles(smiles)[[1]]

#calculate the fragments
fragments <- frag.generateFragments(molecule, 1)

length(fragments)

```

- Input: 
 
 
```{r}
library(uvpd)
library(rawDiag)
#rawfile <- "/Users/cp/data/stds_pos_neg_MS_highconc_UVPD_50_300.raw"
(rawfile <- file.path(Sys.getenv('HOME'), "Downloads",
  "stds_pos_neg_MS_highconc_UVPD_50_300.raw"))
RAW <- read.raw(rawfile, rawDiag = TRUE)
```


```{r}
 table(RAW$MSOrder)
```


## Input


### Get XIC

```{r}
mz <- 296.116
stds_pos_neg_MS_highconc_UVPD_100_150_mz50
# alternative
do.isotopes(molecule)
get.exact.mass(molecule) + 1.007


XIC <- readXICs(rawfile, mz)

plot(XIC)
```

### Get Ms2 Scannumbers

```{r}
eps <- 0.01
sn <- RAW$scanNumber[which(mz-eps< RAW$PrecursorMass & RAW$PrecursorMass < mz + eps)]
```

### Get Ms2 Scans


```{r MS2Scans}
plot.MS2Scans <- function (x, y, ...) 
{
    plot(x$mZ, x$intensity, type = "h", main = x$title, xlab = "m/Z", 
        ylab = "intensity", 
        sub=x$scanType,
        ...)
}

queryScannumbers <- sn[RAW$StartTime[sn] * 60 > 951 & RAW$StartTime[sn] * 60  < 961]
MS2Scans <- readScans(rawfile = rawfile, queryScannumbers)
#lapply(MS2Scans, plot.MS2Scans)
```

# 2019-03-26 
1415-1600 via Skype, FGCZ


## Implement getFragments method

```{r}
# getFragments
```

example call

```{r computeIn-silicoFragments}
df.frags <- getFragments("CC(C)(C)C(O)C(OC1=CC=C(Cl)C=C1)N1C=NC=N1", treeDepth = 1) 
df.frags <- df.frags[!is.na(df.frags$mZ), ]

```

### Plot in-silico spec
```{r in-silico, fig.retina=3}
plot(table(df.frags$mZ))
```


## Compute and Plot Matches

```{r matchPlot, fig.retina=3}
# table.df.frags <- table(df.frags$mZ)

library(protViz)
library(knitr)

write.csv(file='peaklist1.csv', data.frame(mZ=MS2Scans[[1]]$mZ, 
                                           intensity=MS2Scans[[1]]$intensity),
          row.names = FALSE)
```

```{r MS2filtering}
# filtering 


uvpd:::.filterMS2Scans

MS2Scans <- uvpd:::.filterMS2Scans(MS2Scans)

```


```{r match}
rv.match <- matchFragment(MS2Scans, fragments = df.frags, FUN=sum)
kable(rv.match)
```


# 20190415 Analysis

## Read Input

### csv file with SMILES
```{r preparation}

library(readr)
library(uvpd)

ThermoUVPD_feb2019 <- read_csv(file.path(system.file(package = 'uvpd'),
                                         "/extdata/ThermoUVPD_feb2019.csv"))



```

###  Mass Spec generated rawfiles

```{r}
library(ggplot2)
library(parallel)
library(uvpd)
rawfiles <- scan(file.path(system.file(package = 'uvpd'),
                           "/extdata/rawfiles.txt"), what = character())
rawfiles <- rawfiles[grepl("Castell|KWR|DB", rawfiles)]
#rawfiles <- rawfiles[grepl("KWR", rawfiles)]

rawfiles <- rawfiles[!grepl("blank_", rawfiles)]
rawfiles <- rawfiles[!grepl("Blank_", rawfiles)]
rawfiles <- rawfiles[!grepl("neg", rawfiles)]
(rawfiles <- rawfiles[file.exists(rawfiles)])

```

## Extract XICs

```{r extractXICs}
X <- lapply(rawfiles, function(rawfile){
 rv <- try(uvpd:::.extractXICs(rawfile, smiles=ThermoUVPD_feb2019$SMILES, mZoffset=1.007))
})
```


## Compute Matches
```{r numberCrunching, message=FALSE}
S <- lapply(X, function(x){try(uvpd:::.computeMatch(x))})
#S <- do.call('rbind', mclapply(rv, .extractScanNumbers, mc.cores=4))
```


### Trellis
```{r}
SS <- do.call('rbind', S)
library(lattice)
```

```{r}
#table(SS$type)

```

```{r xyplotAll, fig.retina=3, fig.width=30, fig.height=20}
xp <- xyplot(log(intensity, 10) ~ mZ |  basename(rawfile) * SMILES0,
        groups =type, 
         data=SS, 
         type='h')

#print(xp)

```

