
---
title: "20190425"
author: "AB/CP"
output:
  html_document:
    toc_float: true
    toc: true
    number_sections: true
    theme: united
bibliography: uvpd.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load

```{r}
library(uvpd)

load(file.path(system.file(package = 'uvpd'), "/extdata/fragments.RData"))

rawfiles <- scan(file.path(system.file(package = 'uvpd'),
                           "/extdata/rawfiles.txt"), what = character())
rawfiles <- rawfiles[grepl("Castell|KWR|DB", rawfiles)]

```


# Algorithm

## INPUT:

- in-silico fragment ion spectra of a given set of SMILES 
- ThermoFisher raw file

## STEP1: 

- dermines APEX(MS1) of each molecule mass return rt for each given mass; 

## STEP2: 

- extract MS2 at a given rt and precursor window

## STEP3: 

- compute match between in-silico and MS2 fragment specs 

## STEP4: 

- aggregate (default \code{FUN=sum}) matches using
- \code{intensity ~ mZ + type + SMILES + formula}.
 where mZ are the matched fragment ion mass, type is fragment type,e.g., MH1P.

## OUTPUT: 

- a \code{data.frame} object having the column names
\code{c('mZ', 'type', 'SMILES', 'formula', 'intensity', 'rawfile',
   'scanTypeFilter', 'SMILES0', 'formula0', 'mass', 'n'}.

# Example

## INPUT:

### MS2 fragments computed out of the SMILES
```{r}
head(fragments.treeDepth1$SMILES)
head(fragments.treeDepth1$mass)
head(fragments.treeDepth1$ms2[[1]])
```

### Thermo Fisher rawfile

```{r}
(rawfile <- rawfiles[20])
```

## STEP 1-4 

```{r message=FALSE, warning=FALSE}
S <- analyze(rawfile, fragments.treeDepth1)
```



```{r fig.retina=3, fig.width=19, fig.height=12, eval=FALSE}
KWRpos <- lapply(rawfiles[grepl("KWR.+(HCD|UVPD)", rawfiles)], analyze, smiles=ThermoUVPD_feb2019$SMILES)
lapply(KWRpos, function(x){try(uvpd.summary(x))})
    
KWRneg <- lapply(rawfiles[grepl("KWR.+(HCD|UVPD)", rawfiles)], analyze, smiles=ThermoUVPD_feb2019$SMILES, mZoffset=-1.007)
```