---
title: "supplements"
author: "AB/CP"
date: "5/6/2020"
output:
    html_document:
        toc_float: true
        toc: true
        number_sections: true
        theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
```

## Compose

* run `20200416.R`

```{r eval=FALSE}
library(readr)
file_group <- read_csv("file-group.csv")
FG <- file_group[paste(file_group$file, ".raw",sep='') %in% X20200423_uvpd$filename, ]
FG$file <- paste(FG$file, '.raw', sep='')


GS <- data.frame(group=ThermoUVPD_feb2019$Group, SMILES=ThermoUVPD_feb2019$SMILES)
GSF <- merge(GS, FG, by='group')

X20200423_uvpd$m <- paste(X20200423_uvpd$filename, X20200423_uvpd$SMILES)

GSF$m <- paste(GSF$file, GSF$SMILES)


X20200423 <- merge(GSF, X20200423_uvpd, by='m')

```


## Load
```{r}
load(file.path(system.file(package = 'uvpd'), "/extdata/X20200423.RData"))
```


## Sanity check

negative mode

```{r}
knitr::kable(table(X20200423$file[X20200423$mode < 0], X20200423$Group[X20200423$mode < 0]))
```

one substance seems to be part of multiple groups!

positive mode

```{r}
knitr::kable(table(X20200423$file[X20200423$mode > 0], X20200423$Group[X20200423$mode > 0]))
```

lets exclude `"4-Chlorobenzoic acid"`

```{r}
X <- X20200423[!(X20200423$Compound=="4-Chlorobenzoic acid"), ]
knitr::kable(table(X$file[X$mode < 0], X$Group[X$mode < 0]))
knitr::kable(table(X$file[X$mode > 0], X$Group[X$mode > 0]))
```

```{r}
xyplot(log(tic) ~ log(master.intensity) | Compound, groups = fragmode, data=X20200423, pch='.')
```

master intensity =def= masterscan (MS1) isolated precursor m/z intensity in a given mass window +- 0.01 Da.

find three best matches acc. highest master intensity

```{r determinetop3}
# theoretic possible combinations
cc <- expand.grid(as.character(unique(X$file)), as.character(unique(X$SMILES.x)), as.character(unique(X$fragmode)))
names(cc) <- c('file', 'SMILES', 'fragmode')
cc <- paste(cc$file, cc$SMILES, cc$fragmode)

# this is the real world
X$m <- paste(X$file, X$SMILES.x, X$fragmode)

 library(parallel)
X.top3.master.intensity <- do.call('rbind', lapply(cc, function(m){
    XX <- X[X$m == m, ]
    XX <- XX[order(XX$master.intensity, decreasing = TRUE), ]
    n <- nrow(XX)
    
    if (nrow(XX) > 2){
        return(XX[1:3, ])}
    else if (n > 0){
        return(XX[1:n, ])}
    else{return(NULL)}
}))
```

```{r eval=TRUE}
X.top3.tic <- do.call('rbind', lapply(cc, function(m){
    XX <- X[X$m == m, ]
    XX <- XX[order(XX$tic, decreasing = TRUE), ]
    n <- nrow(XX)
    
    if (nrow(XX) > 2){
        return(XX[1:3, ])}
    else if (n > 0){
        return(XX[1:n, ])}
    else{return(NULL)}
}))

```

```{r eval=FALSE}
table(X.top3.master.intensity$file)
table(X.top3.master.intensity$SMILES.x)
table(X.top3.master.intensity$fragmode)
```

```{r}
image(as.matrix(table(X.top3.master.intensity$file, X.top3.master.intensity$fragmode)))
```


compare pos versus negative
TODO(CP): order by reacion time / ce
```{r eval=TRUE}
library(lattice);

lp <- bwplot(log(master.intensity / tic) ~ as.character(mode) | as.factor(fragmode), 
        data=X.top3.master.intensity, horizontal = F)
```

```{r eval=FALSE}
lp <- bwplot(log(master.intensity / tic) ~ as.character(mode) | as.factor(fragmode), 
        data=X.top3.tic, horizontal = F)
```

```{r}
plot(X.top3.tic$scan , X.top3.master.intensity$scan)
```


# fetch MS2

```{r}
library(MsBackendRawFileReader)
```


```{r load_fragments}
load(file.path(system.file(package = 'uvpd'), "/extdata/fragments.RData"))

```


```{r load_protViz}
library(protViz)
```

iterate over a files and compounds ...
```{r define_fragmentMatch}
.fragmentMatch <- function(absoluteErrorCutOffInDalton=0.001, centroid=TRUE){
     lapply(sort(unique(X.top3.master.intensity$file)), function(f){
        sn <- X.top3.master.intensity$scan[X.top3.master.intensity$file==f]
        sm <- X.top3.master.intensity$SMILES.x[X.top3.master.intensity$file==f]
        cm <- X.top3.master.intensity$Compound[X.top3.master.intensity$file==f]
        rawfile <- file.path('/Users/cp/Downloads/p2722/', f)
        message(rawfile)
        x <- .cnew ("Rawfile", rawfile)
        
        rv2 <- mapply(function(scan, smile, compound){
            mZ <- x$GetSpectrumMasses(scan)
            intensity <- x$GetSpectrumIntensities(scan)
            
            if (centroid){
                cc <- protViz::centroid(mZ, intensity)
            }else{
                cc <- data.frame(mZ=mZ, intensity=intensity)
            }
            
            rv <- data.frame(mZ=cc$mZ, intensity=cc$intensity)
            
            # computed by MetFrag
            idx <- which(fragments.treeDepth2$SMILES == as.character(smile))
            insilico <- fragments.treeDepth2$ms2[[idx]]
            insilico <- insilico[!is.na(insilico$mZ),]
            
            # determine best match - assigne in-silico fragment ion to peak
            NN <- findNN(cc$mZ, insilico$mZ)
            absoluteError <- insilico$mZ[NN] - cc$mZ 
            ppmerror <- (abs(absoluteError) /  insilico$mZ[NN]) * 1000000
            
            # filtering but we do not remove yet
            absoluteErrorFilter <- abs(absoluteError) < absoluteErrorCutOffInDalton
            #message(paste(sum(absoluteErrorFilter), "/", length(cc$mZ), "intensity coverage", round(sum(cc$intensity[fff])/sum(cc$intensity),2)))
            
            rv$nPeaks <- length(cc$mZ)
            rv$nAssignedPeaks <- sum(absoluteErrorFilter)
            rv$intensityCoverage <- round(sum(cc$intensity[absoluteErrorFilter])/sum(cc$intensity),2)
            rv$file <- f
            # TODO(cp)
            # rv$formula0 <- NA
            rv$formula <- insilico$formula[NN]
            rv$compound <- compound
            rv$type <- insilico$type[NN]
            rv$eps <- absoluteError
            rv$ppmerror <- ppmerror
            rv$scan <- scan
            #rv$SMILE <- smile
            rv[absoluteErrorFilter, ]
        }, scan=sn, smile=sm, compound=cm, SIMPLIFY = FALSE)
        rv2
    })
}
```


```{r X.top3.master.intensity.MS2}
X.top3.master.intensity.MS2 <- .fragmentMatch(absoluteErrorCutOffInDalton=0.01)
```

TODO(AB): check pos/neg mode in in-silico fragments
```{r}
save(X.top3.master.intensity, X.top3.master.intensity.MS2, file="uvpd.20200514.RData", compression_level = 9)
```

```{r filterAndMergeXY}

X <- X.top3.master.intensity
dim(X)

# list of list to data.frame
Y <- do.call('rbind', do.call('rbind', X.top3.master.intensity.MS2))
dim(Y)
X$m <- paste(X$file, X$scan)
Y$m <- paste(Y$file, Y$scan)
XY <- base::merge(X, Y, by="m")
dim(XY)
```
```{r}
hist(XY$eps)
```

```{r stackedbarcharts, fig.retina=3}
library(ggplot2)
DF <- aggregate(intensity ~ mZ * file.y * fragmode * compound * formula * Group *mode, data=XY, FUN=sum)
dim(DF)
DF$fragmode <- gsub("uvpd50.00", "uvpd050.00", DF$fragmode)
DF$fragmode <- gsub("uvpd25.00", "uvpd025.00", DF$fragmode)


.stackedbarcharts <- function(compound){
    # subsetting
    gp <- ggplot(data = DF[DF$compound == compound, ], 
                 aes(x = fragmode,
                     y = log(intensity, 10),  fill=formula)) +
        geom_bar(stat="identity") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        facet_wrap(~ compound * Group * mode)
    gp
}

.stackedbarcharts("Flubendazole")
```

```{r allstackedbarchart, echo=FALSE, message=FALSE}
compounds <- sort(unique(DF$compound))
lapply(compounds, FUN=.stackedbarcharts)
```


# Session information


```
Rscript -e "rmarkdown::render('supplements.Rmd', output_file='supplements.html')"
```

```{r}
sessionInfo()
```
