---
title: "supplements in-silico"
author: "AB/CP"
date: "June 17, 2020"
output:
    html_document:
        toc_float: true
        toc: true
        number_sections: true
        theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
```


# Load 

```{r}
load(file.path(system.file(package = 'uvpd'), "/extdata/uvpd.20200612.RData"))
```

```{r}

fn <- system.file("extdata/SusDat_Updated_01032018_ID_SMILES.txt", package = "uvpd")
library(readr)
NORMAN <- readr::read_delim(fn,  "\t", escape_double = FALSE, trim_ws = TRUE)

set.seed(1)
smp.size <- 1000
NORMAN.smp <- NORMAN[sample(nrow(NORMAN), smp.size), ]
``` 

# SMILES

```{r}
S <- unique(X.top3.master.intensity[, c('Compound', 'SMILES.x', 'Group')])
S <- S[order(S$Compound), ]
colnames(S) <- c('Compound', 'SMILES', 'Group')
row.names(S) <- 1:nrow(S)
S$SMILES <- as.character(S$SMILES)
knitr::kable(S)
```

## use rcdk 

```{r}
library(rcdk)
mols <- parse.smiles(as.character(S$SMILES))
NORMAN.mols <- parse.smiles(as.character(NORMAN.smp$SMILES))

for (i in mols) {
  try(do.aromaticity(i))
  try(do.typing(i))
  try(do.isotopes(i))
}

for (i in NORMAN.mols) {
  try(do.aromaticity(i))
  try(do.typing(i))
  try(do.isotopes(i))
}

#show(mols[length(mols)])
#show(mols[length(mols)-1])
```


## compute fingerprint; 

```{r}
fps.extended <- lapply(mols, get.fingerprint, type='extended')
NORMAN.fps.extended <- lapply(NORMAN.mols, get.fingerprint, type='extended')
table(sapply(fps.extended, class))

fps.pubchem <- lapply(mols, get.fingerprint, type='pubchem')
#NORMAN.fps.pubchem <- lapply(NORMAN.mols, get.fingerprint, type='pubchem')

#table(sapply(fps.pubchem, class))

#table(sapply(NORMAN.fps.pubchem, class))
```
## Compute Distance Matrix

```{r}
#fpmat.pubchem <- fp.to.matrix(fps.pubchem)   
fp.extended.tanimoto <- fingerprint::fp.sim.matrix(fps.extended, method='tanimoto')
fp.pubchem.tanimoto <- fingerprint::fp.sim.matrix(fps.pubchem, method='tanimoto')

dim(fp.extended.tanimoto);
fp.dist.extended <- as.dist(1 - (fp.extended.tanimoto))
fp.dist.pubchem <- as.dist(1 - (fp.pubchem.tanimoto))
```


## Some distance statistics
```{r fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1, 2))
hist(fp.dist.extended)
hist(fp.dist.pubchem)
```

## Sanity checks 

```{r distplot, fig.retina=3, fig.width=8, fig.height=4}
op <- par(mfrow=c(1, 2))
image(as.matrix(fp.dist.extended))
image(as.matrix(fp.dist.pubchem))
```


```{r hcluster, fig.retina=3, fig.width=8, fig.height=4}
hc.extended <- hclust(fp.dist.extended)#, hang = -0.01, cex = 0.7)
hc.pubchem <- hclust(fp.dist.pubchem) #, hang = -0.01, cex = 0.7)
op <- par(mfrow=c(1, 2))
plot(hc.extended)
plot(hc.pubchem)
```


## k-means

```{r}
ncluster <- 4
set.seed(1) ## kmeans uses a random start
kmc.extended <- kmeans(fp.dist.extended, center = ncluster, iter.max = 100)
table(kmc.extended$cluster)
```
```{r}
set.seed(1) ## kmeans uses a random start
kmc.pubchem <- kmeans(fp.dist.pubchem, center = ncluster, iter.max = 100)
table(kmc.pubchem$cluster)
```

```{r}

library(kohonen)
```

## SOM
```{r}
library(fingerprint)
fpmat_pubchem <- fp.to.matrix(fps.extended) 
```

```{r}
cm <- rainbow(ncluster, alpha=0.5)
G <-somgrid(4, 4, "hexagonal")
So <- som(fingerprint::fp.to.matrix(fps.extended), grid=G)


plot(So, type = 'changes')
plot(So, type="mapping", col = cm[kmc.extended$cluster], pch=16)
#add.cluster.boundaries(So, kmc.extended$cluster)
```
```{r fig.retina=3, fig.height=8, fig.width=8, eval=FALSE}
fpm <- fingerprint::fp.to.matrix(fps.extended)
NORMAN.fps.extended.fpm <- fingerprint::fp.to.matrix(NORMAN.fps.extended)


colors = c('#33333333', 'red')
names(colors) = c('random', 'selected')
lll <- c(rep('random', nrow(NORMAN.smp)), 1:nrow(fpm))
fff <- rbind(NORMAN.fps.extended.fpm, fpm)

G <-somgrid(4, 4, "hexagonal")

So <- som(fff , grid=G)

plot(So, type = 'changes')
plot(So, type="mapping", col = c(rep("grey", nrow(NORMAN.fps.extended.fpm)), cm[kmc.extended$cluster]), pch=16)
#add.cluster.boundaries(So, kmc.extended$cluster)


## t-sne

```{r eval=FALSE}
library(tsne)
```

```{r fig.retina=3, fig.height=8, fig.width=8, eval=FALSE}
fpm <- fingerprint::fp.to.matrix(fps.extended)
NORMAN.fps.extended.fpm <- fingerprint::fp.to.matrix(NORMAN.fps.extended)
NORMAN.fps.pubchem.fpm <- fingerprint::fp.to.matrix(NORMAN.fps.pubchem)


colors = c('#33333333', 'red')
names(colors) = c('random', 'selected')
lll <- c(rep('random', nrow(NORMAN.smp)), 1:nrow(fpm))
fff <- rbind(NORMAN.fps.extended.fpm, fpm)
sss <- sample(nrow(fff))

#ecb = function(x,y){ plot(x,t='n'); text(x,labels=S$Group, col=colors[kmc.extended$cluster]) }

ecb = function(x,y){
    plot(x, type='n')
    points(x[lll == 'random',], pch=16, col='#33333333')
    text(x[lll != 'random',], S$Compound[as.numeric(lll[which(lll != 'random')])], col='red', cex=0.75, srt=0)
}
ecb(tsne_fp)

tsne_fp = tsne(fff, epoch_callback = ecb, perplexity=33, max_iter = 300)
```

# Session information

```
Rscript -e "rmarkdown::render('supplements.Rmd', output_file='supplements.html')"
```

```{r}
sessionInfo()
```
