---
title: "supplements"
author: "AB/CP"
date: "5/6/2020"
output:
    html_document:
        toc_float: true
        toc: true
        number_sections: true
        theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
```

# Merge Theoretical Design 

* run `20200416.R` 
* run `make_X20200612` see file `make-data.R`


# Load 

```{r}
# load(file.path(system.file(package = 'uvpd'), "/extdata/X20200423.RData"))
load(file.path(system.file(package = 'uvpd'), "/extdata/X20200612.RData"))
X20200612 <- X20200612_uvpd
```


## Sanity check 

## Quantitiative Results

negative mode

```{r}
knitr::kable(table(X20200612$file[X20200612$mode < 0], X20200612$Group[X20200612$mode < 0]))
```

one substance seems to be part of multiple groups!

positive mode

```{r}
knitr::kable(table(X20200612$file[X20200612$mode > 0], X20200612$Group[X20200612$mode > 0]))
```

lets exclude `"4-Chlorobenzoic acid"`

```{r makeX}
X <- X20200612[!(X20200612$Compound=="4-Chlorobenzoic acid"), ]
knitr::kable(table(X$file[X$mode < 0], X$Group[X$mode < 0]))
knitr::kable(table(X$file[X$mode > 0], X$Group[X$mode > 0]))
```


```{r fig.retina=3}
bwplot(log(tic/master.intensity) ~  as.factor(mode) |  fragmode ,
       data=X20200612,
       panel = function(x, y, ...){
         panel.bwplot(x, y, ...)
           if (length(x) > 0){
                 rv <- t.test(y~x)
                #message(rv)
                panel.text(1.5, 5,round(rv$p.value, 4), pos=4, cex=0.5)
           }
       })
```

```{r}
xyplot(log(tic) ~ log(master.intensity) | Compound, groups = fragmode, data=X20200612, pch='.')
```

master intensity =def= masterscan (MS1) isolated precursor m/z intensity in a given mass window +- 0.01 Da.

find three best matches acc. highest master intensity

```{r determinetop3}
# theoretic possible combinations
cc <- expand.grid(as.character(unique(X$file)), as.character(unique(X$SMILES.x)), as.character(unique(X$fragmode)))
names(cc) <- c('file', 'SMILES', 'fragmode')
cc <- paste(cc$file, cc$SMILES, cc$fragmode)

# this is the real world
X$m <- paste(X$file, X$SMILES.x, X$fragmode)

 library(parallel)
X.top3.master.intensity <- do.call('rbind', lapply(cc, function(m){
    XX <- X[X$m == m, ]
    XX <- XX[order(XX$master.intensity, decreasing = TRUE), ]
    n <- nrow(XX)
    
    if (nrow(XX) > 2){
        return(XX[1:3, ])}
    else if (n > 0){
        return(XX[1:n, ])}
    else{return(NULL)}
}))
```

```{r determineTop3, eval=FALSE}
X.top3.tic <- do.call('rbind', lapply(cc, function(m){
    XX <- X[X$m == m, ]
    XX <- XX[order(XX$tic, decreasing = TRUE), ]
    n <- nrow(XX)
    
    if (nrow(XX) > 2){
        return(XX[1:3, ])}
    else if (n > 0){
        return(XX[1:n, ])}
    else{return(NULL)}
}))

```

```{r eval=FALSE}
table(X.top3.master.intensity$file)
table(X.top3.master.intensity$SMILES)
table(X.top3.master.intensity$fragmode)
```

```{r}
image(as.matrix(table(X.top3.master.intensity$file, X.top3.master.intensity$fragmode)))
```


compare pos versus negative
TODO(CP): order by reacion time / ce
```{r eval=TRUE}
library(lattice);

lp <- bwplot(log(master.intensity / tic) ~ as.character(mode) | as.factor(fragmode), 
        data=X.top3.master.intensity, horizontal = F)
```

```{r eval=FALSE}
lp <- bwplot(log(master.intensity / tic) ~ as.character(mode) | as.factor(fragmode), 
        data=X.top3.tic, horizontal = F)
```

```{r eval=FALSE}
plot(X.top3.tic$scan , X.top3.master.intensity$scan)
```


## Fetch Fragment Ions (MS2)

```{r}
library(MsBackendRawFileReader)
```

## Load Predicted Fragment Ions

```{r load_fragments}
load(file.path(system.file(package = 'uvpd'), "/extdata/fragments.RData"))

fragmentsPredicted <- as.data.frame(do.call('rbind', lapply(fragments.treeDepth1$ms2, function(x){table(x$type)})))

fragmentsPredicted$formula <- fragments.treeDepth1$formula
```


```{r load_protViz}
library(protViz)
```

* iterate over a files and compounds ...
* fetch related MS2 scans using rawDiag
* assign predicted fragment ion annotation

```{r define_fragmentMatch}

RAWFILEDIR <- '/Users/cp/Downloads/p2722/'

.fragmentMatch <- function(absoluteErrorCutOffInDalton=0.01, centroid=TRUE){
     lapply(sort(unique(X.top3.master.intensity$file)), function(f){
        sn <- X.top3.master.intensity$scan[X.top3.master.intensity$file==f]
        sm <- X.top3.master.intensity$SMILES.x[X.top3.master.intensity$file==f]
        cm <- X.top3.master.intensity$Compound[X.top3.master.intensity$file==f]
        rawfile <- file.path(RAWFILEDIR, f)
        message(paste("processing rawfile", rawfile, "..."))
        x <- .cnew ("Rawfile", rawfile)
        
        rv <- mapply(function(scan, smile, compound){
            mZ <- x$GetSpectrumMasses(scan)
            intensity <- x$GetSpectrumIntensities(scan)
            
            if (centroid){
                cc <- protViz::centroid(mZ, intensity)
            }else{
                cc <- data.frame(mZ=mZ, intensity=intensity)
            }
            
            DF <- data.frame(mZ=cc$mZ, intensity=cc$intensity)
            
            # computed by MetFrag and stored in the uvpd package
            idx <- which(fragments.treeDepth1$SMILES == as.character(smile))
            insilico <- fragments.treeDepth1$ms2[[idx]]
            insilico <- insilico[!is.na(insilico$mZ),]
            
            # determine best match - assigne in-silico fragment ion to peak
            NN <- findNN(cc$mZ, insilico$mZ)
            absoluteError <- insilico$mZ[NN] - cc$mZ 
            ppmerror <- (abs(absoluteError) /  insilico$mZ[NN]) * 1000000
            
            # filtering but we do not remove yet
            absoluteErrorFilter <- abs(absoluteError) < absoluteErrorCutOffInDalton
            
            DF$nPeaks <- length(cc$mZ)
            DF$nAssignedPeaks <- sum(absoluteErrorFilter)
            DF$intensityCoverage <- round(sum(cc$intensity[absoluteErrorFilter])/sum(cc$intensity),2)
            DF$file <- f
            # TODO(cp)
            # rv$formula0 <- NA
            DF$formula0 <- fragments.treeDepth2$formula[idx]
            DF$formula <- insilico$formula[NN]
            DF$compound <- compound
            DF$type <- insilico$type[NN]
            DF$eps <- absoluteError
            DF$ppmerror <- ppmerror
            DF$scan <- scan
            #rv$SMILE <- smile
            DF[absoluteErrorFilter, ]
        }, scan=sn, smile=sm, compound=cm, SIMPLIFY = FALSE)
        rv
    })
}
```

### Filter
```{r X.top3.master.intensity.MS2}
X.top3.master.intensity.MS2 <-.fragmentMatch(absoluteErrorCutOffInDalton=1.0)
```


# Compose Result Table
TODO(AB): check pos/neg mode in in-silico fragments

```{r eval=FALSE}
save(X.top3.master.intensity, X.top3.master.intensity.MS2, file="uvpd.20200612.RData", compression_level = 9)
```

```{r filterAndMergeXY}
X <- X.top3.master.intensity
dim(X)

# list of list to data.frame
Y <- do.call('rbind', do.call('rbind', X.top3.master.intensity.MS2))
dim(Y)
X$m <- paste(X$file, X$scan)
Y$m <- paste(Y$file, Y$scan)
XY <- base::merge(X, Y, by="m")
dim(XY)
```

## Sanity checks

absolute error
```{r absoluteError}
hist(XY$eps)
```

```{r}
table(XY$type, XY$mode)
```

```{r}
table(XY$type, XY$Group)
```

```{r}
knitr::kable(fragmentsDetected <- (table(XY$formula0, XY$type)))
```

## Stacked Bar Charts

```{r fig.width=20}
bwplot(ppmerror ~ fragmode | compound, data=XY, scales = list(x = list(rot = 45)))
```

```{r stackedbarcharts, fig.retina=3}
library(ggplot2)

DF <- aggregate(intensity ~ mZ * file.y * fragmode * compound * formula * Group *mode, data=XY[XY$ppmerror<20,], FUN=sum)
dim(DF)
DF$fragmode <- gsub("uvpd50.00", "uvpd050.00", DF$fragmode)
DF$fragmode <- gsub("uvpd25.00", "uvpd025.00", DF$fragmode)
#levels(DF$fragmode) <- unique(DF$fragmode)

.stackedbarcharts <- function(DF, compound = "Triadimenol"){
    S <- DF[DF$compound == compound, ]
    gp <- ggplot(data = S,
                 aes(x = factor(fragmode, levels = sort(unique(DF$fragmode))),
                     y = log(intensity, 10),
                     fill=reorder(formula, mZ))) +
        geom_bar(stat="identity", position = position_stack(reverse = FALSE)) +
        scale_x_discrete(drop=FALSE) +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        facet_wrap(~ compound * Group * mode, scales="free", drop=FALSE)

   # gp2 <- ggplot(data=unique(subset(S, select=c('fragmode','formula'))), aes(x=factor(fragmode, levels = sort(unique(DF$fragmode))), fill=(formula))) + ggplot2::geom_bar()
   gp
}

.stackedbarcharts(DF, compound = "Flubendazole")
.stackedbarcharts(DF, compound = "Triadimenol")
```

```{r allstackedbarchart, echo=FALSE, message=FALSE}
compounds <- sort(unique(DF$compound))
lapply(compounds, FUN=.stackedbarcharts, DF=DF)
```

# Session information

```
Rscript -e "rmarkdown::render('supplements.Rmd', output_file='supplements.html')"
```

```{r}
sessionInfo()
```
